%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-deedy}

%%% Override a directory location for fonts(default: 'fonts/')
%\fontdir[../fonts]

%%% Configure a directory location for sections
%\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
%\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{import}
\import{}{personal-details.tex}
\quote{``Its only impossible until someone finds a way."}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Human Resources}
  {University of New South Wales \\ Sydney NSW, 2052}
\letterdate{\today}
\lettertitle{Job Application for Research Assistant (55891)}
\letteropening{To whom it may concern,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Matthew McGill~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}

I am writing to you today to apply for the position of Research Assistant at the University of New South Wales.  I feel that I am well suited for this role as I have worked with a wide variety of autonomous robots including search and rescue, humanoid and sailing.  As a result I have had experience with many aspects of robotics such as speech recogniton, user interface, software and hardware mantenaince, mapping and localisation, navigation and planning. 

\section{About Me}

I have worked at the University of New South Wales(UNSW) for 12 years on a variety of projects.  These projects include a system for responding to spoken and multi-modal gestures, developing robots for search and rescue applications.  During this time I represented UNSW at a a number of international competitions and at workshops and conferences.  While at UNSW I also lectured and taught courses on developing software for robots, including the use of the Robot Operating System (ROS).

Prior to moving to Sydney I recieved my Bachelor of Information Technology from the University of Queensland before working as a research assistant for 2 years examining factors affecting human comprehension of UML diagrams.

%\section{Why UNSW}

\section{Why Me?}

I believe I am well suited to this position as I have worked with a large variety of robots including wheeled, tracked and humanoid.  I have experience developing robotics software using a variety of programming languages such as C++, python and Java.

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
