%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-deedy}

%%% Override a directory location for fonts(default: 'fonts/')
%\fontdir[../fonts]

%%% Configure a directory location for sections
%\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
%\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{import}
\import{}{personal-details.tex}
\quote{``Its only impossible until someone finds a way."}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Human Resources}
  {University of New South Wales \\ Sydney NSW, 2052}
\letterdate{\today}
\lettertitle{Selection Criteria for Research Assistant (55891)}
\letteropening{To whom it may concern,}
\letterclosing{Sincerely,}
%\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Matthew McGill~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}

\section{Research Experience}

My research experience invloves a number of jobs at the University of New South Wales(UNSW) and the University of Queensland(UQ).  This is as both a research assistant at UQ and a researcher at UNSW.

\section{Development Experience in Multiple OSs}

I have developed software in multiple languages for a number of operating systems. I have produced applications in C/C++, Java and Python that run on Windows, Linux and OS X.

\section{C/C++ Skills}

I have worked on a number of software tools that were written in C/C++.  These include a speech recognition server and multiple systems running on autonomous vehicles. 

\section{Knowledge of Autonomous Vehicles}

I have worked with a variety of autonomous and semi-autonomous robots.  This includes representing UNSW at RoboCup as part of team CASualty in the Rescue Robot League.
This involved working with both wheeled and tracked robots.  I have also worked with humanoid robots such as the soccer playing Naos and the research oriented Baxter robot. 

\section{Sailing Experience}

I have spent 3 months working with Ocius on an unmanned sailing vessel.  Prior to this as a child I spent many days sailing on my family's catamaran.

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
